```{r setup, include=FALSE}
library(caret)
library(ggplot2)
```

#Load the data
```{r}
diabetes <- read.csv('diabetes.csv')
```

#View the Diabetes dataset, first 6 rows and structure of the dataset after removing any NA values
```{r}
diabetes <- na.omit(diabetes)

head(diabetes)
str(diabetes)
```

#Understand variable relation with correlation matrix
```{r}
corDiabetes<-cor(diabetes[1:9], use="complete.obs", method="pearson")
round(corDiabetes, 2)
```

#Based on the correlation matrix, we can see the Glucose has the highest correlation. This shows that if someone has a higher glucose level, their chance of diabetes goes up. BMI is the next highest which shows that BMI is also a contributing factor. 

#Barplot showing diabetes vs non diabetes
```{r}
ggplot(diabetes, aes(x=Outcome, y=Age, fill=Outcome)) + 
       geom_bar(stat="identity", width= 1) + theme_minimal() + ggtitle("Age") + xlab("Outcome") + ylab("Age")
```



#Split into train and test datasets, Diabetes
#View the dimensions of the train and test datasets to verfiy it was split at approximately the right percentage
```{r}
set.seed(1000)
trainIndex <- createDataPartition(diabetes$Outcome, p = .8, 
                                  list = FALSE, 
                                  times = 1)
diabetesTrain <- diabetes[ trainIndex,]
diabetesTest  <- diabetes[-trainIndex,]

dim(diabetesTest) #Test
dim(diabetesTrain) #Train
```

#

model.lr1 <- lm(Outcome ~ ., diabetesTrain)
model.lr1
summary(model.lr1)
RMSE(model.lr1$fitted.values, Outcome)

aic <- AIC(model.lr1)
bic <-BIC(model.lr1)

pred.model.lr1 <- predict(model.lr1, newdata = diabetesTest) # validation predictions
meanPred <- mean((diabetesTest$Outcome - pred.model.lr1)^2) # mean prediction error
stdError <- sd((diabetesTest$Outcome - pred.model.lr1)^2)/length(diabetesTest$Outcome) # std error

modelMetrics <- data.frame( "Model" = character(), "adjRsq" = integer(),  "AIC"= integer(), "BIC"= integer(), "Mean Prediction Error"= integer(), "Standard Error"= integer(), stringsAsFactors=FALSE)

modelMetrics[nrow(modelMetrics) + 1, ] <- c( "model.lr1", 0.279, aic, bic, meanPred, stdError)
modelMetrics

model.fit <- lm(Outcome ~ Glucose, data = diabetes)
RMSE(model.fit$fitted.values, Outcome)
